XOR-Some Prolific Pilot 1

### 2021-03-28 analysis/xor-some-prolific-pilot1.Rmd
check by-participant performance

>>>>

Check by-participant behavior to see if they show versatile response strategies for the different questions for xor vs. some. Participants show a sufficient range of responses across conditions.  
```{r, fig.width=15, fig.height=7}
d_critical %>%
  filter(block == class_condition | block == "xor" | block == "some") %>%
  ggplot(., aes(x = block, y = response, color = block)) +
  geom_point(alpha = 0.7, size = 2) + 
  facet_wrap(main_type~submission_id, ncol = 10) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("By-participant ratings all xor vs. some trials")
```
